### 2008-09-15 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

\section{Implications for the System}
Now, if $T_i$ and $T_j$ do not either modify the data the other one uses, according to Rule 4 both can commit. This means even if $T_i$ accesses $tr_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit. \\

@@

proof: Due to assumtion 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different. According to Def 2 it uses the data\\

@@

>>>>

\section{Implications for the System}

\subsection{General Principles}
Now, if $T_i$ and $T_j$ do not either modify the data the other one uses, according to Rule 4 both can commit. This means even if $T_i$ accesses $tr_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit. \\

@@

proof: Due to assumption 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different. According to Def 2 it uses the data\\

@@

\subsection{A Model for Offset and Data Dependeny for Operations}
